### 2019-03-27 micro4_3.tex
Micro

	\section*{Flexibility}
		Since flexibility is always good, an employer who does not know the worker's productivity
		will benefit from adjusting the contract after the worker reveals his productivity. Discus

@@

		I donít want to complain, but my favourite lunchtime haunt has the rudest barman I've
		ever encountered - and I don't think it's an accident. The restaurant is famous for its
		superb, sophisticated Italian cooking and it prices accordingly. A romantic meal for two
		costs about \$150, plus the price of your selection from a wine list of biblical proportions.
		Even if you pick the cheapest main course for lunch and sip water, this frugal meal for
		one will set you back \$15.
		Or, you could sit at the bar or on one of the tables in the bar area. The food is still
		superb: you can fill up on rich, soft pork meatballs nestling on pillows of light polenta for
		about \$8. The veal ragu is rich but you don't have to be, because this perfect spaghetti
		is half the price of a pasta dish in the main restaurant.
		It sounds too good to be true, and I'm afraid there is a catch. To get to the food,
		you have to get past the barman who takes your orders, a man more Bond villain than
		bon vivant. To walk into that bar is to laugh in the face of fear. The barman welcomes
		me in with all the warmth of a Transylvanian butler in a B-movie. He drops menus on
		my table with a sneer. He repeatedly ignores my attempts to order. As he walks past,
		my companion whispers that he picked up his tattoos in a Russian prison. I think sheís
		having me on, but I canít be sure.
		Itís possible, of course, that this man is in the wrong job by accident, and when
		the restaurant owner reads this column and works out that itís about his restaurant,
		"Igor" will be fired. I'm not convinced. I think Igor is all part of the plan. One food
		critic described a previous bartender as acting like sheíd just returned from a tax audit.
		"Venomous" is obviously in the job description.
		Why would a restaurant deliberately sabotage the dining experience?
\end{document}

>>>>

	\section*{5 Flexibility}
		Since flexibility is always good, an employer who does not know the worker's productivity
		will benefit from adjusting the contract after the worker reveals his productivity. Discus

		In some sense employer indeed benefits from renegotiation of the labour contract, because it can implement the most efficient contract. But in the long run such an opportunity can harm the employer because of the following reason. The employer will renegotiate the contract only with the low productivity worker, because the initial contract with this type of workers was deliberately worse than it could be, in order to prevent the high productivity type from pretending to be low. But if ex-ante the high productivity worker had known that tomorrow contract with low type is renegotiated, he would not have reveled his type, and still would have chosen to pretend being of low type. That is, in short run the employer can benefit, but in the long run without commitment he will lose, because nobody of the high type wants to reveal their type.

@@

		I don't want to complain, but my favourite lunchtime haunt has the rudest barman I've
		ever encountered - and I don't think it's an accident. The restaurant is famous for its
		superb, sophisticated Italian cooking and it prices accordingly. A romantic meal for two
		costs about \$150, plus the price of your selection from a wine list of biblical proportions.
		Even if you pick the cheapest main course for lunch and sip water, this frugal meal for
		one will set you back \$15.
		Or, you could sit at the bar or on one of the tables in the bar area. The food is still
		superb: you can fill up on rich, soft pork meatballs nestling on pillows of light polenta for
		about \$8. The veal ragu is rich but you don't have to be, because this perfect spaghetti
		is half the price of a pasta dish in the main restaurant.
		It sounds too good to be true, and I'm afraid there is a catch. To get to the food,
		you have to get past the barman who takes your orders, a man more Bond villain than
		bon vivant. To walk into that bar is to laugh in the face of fear. The barman welcomes
		me in with all the warmth of a Transylvanian butler in a B-movie. He drops menus on
		my table with a sneer. He repeatedly ignores my attempts to order. As he walks past,
		my companion whispers that he picked up his tattoos in a Russian prison. I think she's
		having me on, but I can't be sure.
		It's possible, of course, that this man is in the wrong job by accident, and when
		the restaurant owner reads this column and works out that it's about his restaurant,
		"Igor" will be fired. I'm not convinced. I think Igor is all part of the plan. One food
		critic described a previous bartender as acting like she'd just returned from a tax audit.
		"Venomous" is obviously in the job description.
		Why would a restaurant deliberately sabotage the dining experience?

		It is an example of the second degree price discrimination. Unless existence of Igor, everybody went to the bar, get the same, superb food, but paying less. But the firm wants to separate those who can pay more from those who cannot afford going to the restaurant and reserving tables. To do so, the contracts the restaurant proposes should be incentive compatible. That is, the rich guys should not have incentives to deviate and to go to the bar and "underpay". Hence the owner of the restaurant has to decrease the quality of serving in bar, in order to prevent rich guys from going there.

		\section*{7 Revelation Principle}
			The revelation principle is a very powerful tool that greatly simplifies the search for optimal
			mechanisms. Think about the intuitive argument and the logic behind the revelation principle
			and, importantly, the assumptions this argument implicitly makes. Suggest a real-life situation
			where the revelation principle would fail. Explain why the logic of the revelation principle
			cannot be applied to your example.

			The principle is based on the idea that even if instead of reporting type 
\end{document}
